Datasheet for 'New York Bridge 2016

### 2024-12-04 other/datasheet/datasheet.qmd
Add a reference

The **New York Bridges 2016 dataset** should not be used for tasks requiring real-time data analysis or dynamic decision-making, as it represents a static snapshot of bridge conditions as of 2016. It is unsuitable for assessing current structural risks or predicting immediate failures without incorporating updated data. Additionally, the dataset should not be used for commercial purposes that could conflict with public interests, such as privatization analyses aimed at reducing public access to infrastructure. Finally, it is not appropriate for applications requiring sensitive or individualized data, as it does not contain personal information or real-time monitoring details.

**Distribution**
The New York Bridges 2016 dataset is publicly available and distributed through the Data and Story Library (DASL) website. It is accessible as a downloadable file in common formats such as text or CSV, ensuring ease of use for researchers and policymakers. The dataset does not have a dedicated digital object identifier (DOI), but it is maintained under publicly available terms, which can be accessed directly from the DASL platform.

>>>>

The New York State Bridge Conditions dataset, also utilized in the ARTBA's bridge report[@ARTBA], has been applied to analyze the structural conditions of bridges across New York. The dataset helps identify structurally deficient bridges, prioritize infrastructure projects, and allocate federal funds, such as the $2 billion bridge formula funds under the Infrastructure Investment and Jobs Act (IIJA). This dataset is well-suited for tasks like policy development, maintenance scheduling, risk assessment, and infrastructure planning, offering actionable insights into bridge management. However, its composition reflects current bridge conditions and may not fully account for recently completed repairs, which could influence its applicability for real-time analyses. The dataset is tailored to infrastructure evaluations and is not recommended for unrelated uses. Overall, it serves as a critical resource for understanding and improving bridge conditions in New York State.

This dataset should not be used for tasks requiring real-time data analysis or dynamic decision-making, as it represents a static snapshot of bridge conditions as of 2016. It is unsuitable for assessing current structural risks or predicting immediate failures without incorporating updated data. Additionally, the dataset should not be used for commercial purposes that could conflict with public interests, such as privatization analyses aimed at reducing public access to infrastructure. Finally, it is not appropriate for applications requiring sensitive or individualized data, as it does not contain personal information or real-time monitoring details.

**Distribution**

The New York Bridges 2016 dataset is publicly available and distributed through the Data and Story Library (DASL) website. It is accessible as a downloadable file in common formats such as text or CSV, ensuring ease of use for researchers and policymakers. The dataset does not have a dedicated digital object identifier (DOI), but it is maintained under publicly available terms, which can be accessed directly from the DASL platform.
